### 2017-03-30 thesis/latex/thesis.tex
Thesis: add work on intro. Also add figures-to-make list.

>>>>

\subsection{Interest builder}
Motor proteins are cellular structures which use chemical energy to do work and generate motion. Kinesin, myosin and dynein are the three main motor proteins in cells. Though these proteins have significantly different ancestors [cite], they all evolved into a single similar structure. In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem. How, then, do motor proteins work?\\

The basic form is simple. Kinesin, myosin and dynein each have two foot domains which each alternatingly act as levers. One foot will bind to a surface and apply a force, levering the whole motor forward. This causes the other foot to bind and the cycle to repeat. This design is simple, but the ways each motor implement it are very different. Binding to the .........

Dynein:
feet which bind to track
motor connected to feet which generates the force
-----------
ATP binding causes dissociation
Also causes forward kick
ATP hydrolysis
rebinding causes ADP rejection and forward lurch
restart

Kinesin:
feet which bind to track
connected via lever arm to cargo binding domain
-----------
ATP binding causes forward kick
ATP hydrolysis
MT binding, ADP, Pi rejection
Other foot unbinds

Myosin:
Feet which bind to track
connected via lever arm to cargo binding domain
----------
actin binding causes Pi rejection, strengthening binding
binding causes foot to change relative to lever, shifting the motor forward
ATP binding causes dissocaition and undoing the powerstroke

Todo:
figure out how myosin works
explain how the motors are all really similar in structure
also how they're all kind of carnot-like engines which take in energy and do work
explain how dynein is much more stochastic than kinesin, and how this is interesting, since it hints at a Brownian component, which isn't present in kinesin
Talk about how confirming brownian component of the cycle would be good
